Parameterization of the responses of subarctic European vegetation to key environmental variables for ozone risk assessment

### 2022-05-12 VegOzone.tex
Small update

Taking a presumed adaption of vegetation to local climate into consideration, we derived localized Jarvis-type temperature and light response functions for modeling $\mathrm{POD_1}$ and biomass reduction with the $\mathrm{DO_3SE}$ model. Our key findings are that vegetation that is more sensitive to warm temperatures would be less effected by coincident ozone and heat stress because stomata will close to prevent water loss whereas vegetation adapted to warmer climate zones could be under higher ozone damage risk under these conditions. On the other hand, a warmer climate and hence prolonged GS would negatively affect any vegetation using the $\mathrm{POD_y}$ metric. It is essential for ozone risk assessments in the subarctic to define plant physiology and traits such as phenological states properly. As no independent ozone flux measurements are available at Svanhovd, we could not fully validate our methodology at this point. 
A comparison of $\mathrm{DO_3SE}$ model derived dry deposition velocities $V_\mathrm{d}$ for coniferous trees with comprehensive records over Pine forests from Hyytilälä, Finland \citep{BER:Keronen2003} (refer to supplementary material Figs.~S1--S3) indicate a slightly too high $V_\mathrm{d}$ in spring for our most extreme localization (subarctic). No comparable data is available for northern Fennoscandia or deciduous tress and perennial grassland. Perennial grassland and deciduous trees displayed strong susceptibility to our localization methodology (increase in frequency of maximum $V_\mathrm{d}$ throughout the GS, see supplementary material Figs.~S1--S3) but are within the range given in the literature \citep[e.g.][]{JGR:Jacob1992,AE:Padro1996,RG:Clifton2020}. Independent flux measurements over these vegetation types in a subarctic climate are thus crucial for evaluation and validation.

>>>>

Taking a presumed adaption of vegetation to local climate into consideration, we derived localized Jarvis-type temperature and light response functions for modeling $\mathrm{POD_1}$ and biomass reduction with the $\mathrm{DO_3SE}$ model. Our key findings are that vegetation that is more sensitive to warm temperatures would be less effected by coincident ozone and heat stress because stomata will close to prevent water loss whereas vegetation adapted to warmer climate zones could be under higher ozone damage risk under these conditions. On the other hand, a warmer climate and hence prolonged GS would negatively affect any vegetation using the $\mathrm{POD_y}$ metric. It is essential for ozone risk assessments in the subarctic to define plant physiology and traits such as phenological states properly. As no independent ozone flux measurements are available at Svanhovd, we could not fully validate our methodology at this point. 
A comparison of $\mathrm{DO_3SE}$ model derived dry deposition velocities $V_\mathrm{d}$ for coniferous trees with comprehensive records over Pine forests from Hyytilälä, Finland \citep{BER:Keronen2003} (refer to supplementary material Figs.~S1--S3) indicate a slightly too high $V_\mathrm{d}$ in spring for our most extreme localization (subarctic). No comparable data is available for northern Fennoscandia or deciduous tress and perennial grassland. Perennial grassland and deciduous trees displayed strong susceptibility to our localization methodology (increase in frequency of maximum $V_\mathrm{d}$ throughout the GS, see supplementary material Figs.~S1--S3) but are within the range ($v\mathrm{d} = (2-9)\,\unit{mm\,s^{-1}}$ for grassland) given in the literature \citep[e.g.][]{JGR:Jacob1992,AE:Padro1996,RG:Clifton2020}. Independent flux measurements over these vegetation types in a subarctic climate are thus crucial for evaluation and validation.
